---
title: "Simple knitr Rmarkdown example --- automatic write-up of simulated data"
author: "Author name goes here"
output:
  pdf_document: default
  html_document:
    df_print: paged
fontsize: 12pt
---

<!-- This is a comment 
     The following code alternates betwen R and the write-up of text
-->

<!-- <!-- knitr options, adapted from gfsynopsis: --> -->
<!-- ```{r setup, echo=FALSE, cache=FALSE, message=FALSE, results='hide', warning=FALSE} -->
<!-- knitr::opts_chunk$set( -->
<!--   collapse = TRUE, -->
<!--   # warning = FALSE, -->
<!--   # message = FALSE, -->
<!--   comment = "#>", -->
<!--   fig.path = "knitr-figs/", -->
<!--   cache.path = if (knitr:::is_latex_output()) "knitr-cache-tex/" else "knitr-cache-docx/", -->
<!--   fig.asp = 0.618, -->
<!--   fig.width = 9, -->
<!--   out.width = "6in", -->
<!--   echo = TRUE, -->
<!--   autodep = TRUE, -->
<!--   cache = TRUE, -->
<!--   # cache.comments = FALSE, -->
<!--   dev = if (knitr:::is_latex_output()) "pdf" else "png", -->
<!--   dpi = 200, -->
<!--   fig.align = "center", -->
<!--   fig.pos = "htb" -->
<!-- ) -->
<!-- ``` -->

The point of this is to introduce the idea of *dynamically generated
reports*. There'll be some formatting syntax to pretty it up, but don't worry
about that too much.

## Generate data

We wish to generate some data and create a summary of the statistics. 
First generate the data in R:

```{r generate}
set.seed(42)
n <- 50 # sample size
x <- 1:n
y <- 10 * x + rnorm(n, 0, 10)
# y = 10*x^1.5 + rnorm(n, 0, 10)
n
```

So that runs the R code, prints it plus any output.

We can also embed results from R within sentences: 

We have a sample size of `r n`.

The maximum value of $y$ is `r max(y)`.

Or round it to two decimal places: the maximum value of $y$ is `r round(max(y),2)`.

## Not show the R code

We can choose *not* to echo the R code:

```{r notecho, echo=FALSE}
# library(kableExtra)
library(dplyr)
library(xtable)
z <- 37
```

## Show some data

Show some values:

```{r showdata}
data <- tbl_df(cbind(x, y))
data
```

(only the first 10 rows get printed here thanks to dplyr).

<!-- This forces all floating tables and figures to appear and starts a new page in Latex. Only applies to PDF output.-->
\clearpage 

## Plot the data

Now we want to plot the data:

```{r plot}
plot(x, y)
```

\clearpage

## Now to fit a linear regression

Can fit and then print the summary regression output from R:

```{r regression}
fit <- lm(y ~ x)
print(summary(fit))
``` 

And create a plot:

```{r plotfit}
plot(x, y)
abline(fit, col = "red")
```

## Summarise the results

So the maximum value of $y$ is `r round(max(y),0)`, which is 
`r ifelse(max(y)>400, paste("greater than"), paste("less than"))` 
the special value of 400.

So you can actually somewhat automate the text (just be careful and think about
other possibilities -- what if $y=399.9$ in the above example?).

So you can automate a sentence such as "the stock is in the healthy zone". 

## Now, let's go back and change the data

The *big* feature of dynamically generating reports is when you go back and 
change or update the input data.

Let's go back and change replace the definition of $y$ with
```{r changey, eval=FALSE}
y <- 10 * x^1.5 + rnorm(n, 0, 10)
```

[I'll do this manually].

Look at the `.Rmd` code here and note the ues of `eval=FALSE`.

# Exercises:

1. Get the code running.

2. Change `n` to 30, and re-run.

3. Hide the output in the first chunk of the 'Now to fit a linear regression' 
section. (In a report you wouldn't show such results, though it's very useful
when exploring data -- I show the output all the time when looking at large data
frames).

\clearpage

## Explain cache

1. Look at `knitr-cache-tex/` folder, order files by 'Date modified'.

2. Re-run this file. Look at the times of those files.

3. Change $n$ back to 50.

4. Re-run this file. Again look at the times of the files in `knitr-cache-tex/`.

So `knitr` caches results of each chunk, but then re-runs those that have
changed (or those that depend on something that has change).

Very efficient --- if you just update some text you don't need all the
calculations redone.

Beware --- if you read in, say, a `.csv` file and the contents of the file change,
`knitr` will still use the cached read-in of that file, because it won't know
that the file has changed. 

If you're not sure then it's safest to delete the `knitr-cache-tex/` directory 
to re-run all calculations (including loading in of data).


