---
# rmarkdown::render("knitr-example.Rmd")
title: Simple knitr Rmarkdown example -- automatic write-up of simulated data
author: "Author name goes here"
output: pdf_document
fontsize: 12pt
header-includes:
  - \usepackage{mathptmx}      # Better font
  # Need these packages for kableExtra - if hard to download 
  #  then use knitr-example-2.Rmd for simpler version of this file
  - \usepackage[table]{xcolor}
  - \usepackage{colortbl}
  - \usepackage{booktabs}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}

---

The point of this is to introduce the idea of *dynamically generated
reports*. There'll be some formatting syntax to pretty it up, but don't worry
about that too much.

## Generate data

We wish to generate some data and create a summary of the statistics. 
First generate the data in R:

```{r}
set.seed(42)
n = 50                       # sample size
x = 1:n               
y = 10*x + rnorm(n, 0, 10)
# y = 10*x^1.5 + rnorm(n, 0, 10)
n
```

So that runs the R code, prints it plus any output.

We can also embed results from R within a sentence: 

We have a sample size of `r n`.

The maximum value of $y$ is `r max(y)`.

Or round it to two decimal places: the maximum value of $y$ is `r round(max(y),2)`.

## Not show the R code

We can choose *not* echo the R code:

```{r, echo=FALSE}
library(kableExtra)
library(dplyr)
library(xtable)
```

## Show some data

Show some values:

```{r}
data = tbl_df(cbind(x, y))
data
```

(only the first 10 rows get printed here thanks to dplyr).

To have a proper table:
```{r}
kable(data[1:10,],
      caption = "The first rows of my data.") %>%
    kable_styling(latex_options = "h")    
```

<!-- This is a comment, done using the HTML syntax for comments -->

<!-- The option "h" above is just to force the table to appear 'here' in the
output, over-riding the default to put it somewhere more sensible (top, or next
page). 
--> 


\clearpage

The default is a little ugly, but we can tweak some settings:
```{r}
kable(data[1:10,],
      caption = "The first rows of my data, with better formatting.",
      booktabs = TRUE) %>%
    kable_styling(latex_options = c("striped", "h"))
```

But we won't get into that now (just so you know that pretty much everything is 
tweakable).

\clearpage

## Plot the data

Now we want to plot the data:

```{r}
plot(x, y)
```

\clearpage

## Now to fit a linear regression

Can fit and then print the summary regression output from R:

```{R}
fit = lm(y~x)
print(summary(fit))
``` 

Can produce a simple table of output and the regression fit:

```{R}
kable(coefficients(summary(fit)),
      caption = "Linear regression fit.",
      booktabs = TRUE) %>%
    kable_styling(latex_options = "h")    
```

And create a plot:
```{R}
plot(x, y)
abline(fit, col="red")
```

## Summarise the results

So the maximum value of $y$ is `r round(max(y),2)`, which is 
`r ifelse(max(y)>400, paste("greater than"), paste("less than"))` 
the special value of 400.

So you can actually somewhat automate the text (just be careful and think about
other possibilities -- what if $y=399.9$ in the above example?).

So you can automate a sentence such as "the stock is in the healthy zone". 

## Now, let's go back and change the data

The *big* feature of dynamically generating reports is when you go back and 
change or update the input data.

Let's go back and change replace the definition of $y$ with
```{r, eval=FALSE}
y = 10*x^1.5 + rnorm(n, 0, 10)
```

[I'll do this manually].

Look at the `.Rmd` code here and note the ues of `eval=FALSE`.

Exercises:

1. Get the code running.

2. Change `n` to 30, and re-run.

3. Hide the output in the first chunk of the 'Now to fit a linear regression' 
section. (In a report you wouldn't show such results, though it's very useful
when exploring data -- I show the output all the time when looking at large data
frames).

4. ME - use cache=TRUE (that's why it's a bit slow I think...). Add chunk names.






<!--


<<table, results=tex, echo=FALSE>>=
print(xtable(matrix(y, ncol=5, byrow=TRUE), digits = 2, caption="Generated values of $y$.", label=paste("tab:data")))

print(xtable(cbind(x[1:20],y[1:20]), caption="First 20 generated values of $x$ and $y$.", label=paste("tab:first20")))
@ 

\clearpage

So what about the maximum value of $y$?
<<max, echo=TRUE>>=
max(y)
@ 

But a neater way is to embed it in the text:

The maximum value of $y$ is \Sexpr{round(max(y), 2)} to 2 decimal places.

The maximum is \Sexpr{if(max(y)>50) paste("greater than") else paste("less than or equal to")} 50.

<<echo=FALSE, results=hide>>=
fig.name = "data"
postscript(paste(fig.name, ".eps", sep=""), horizontal=FALSE, paper="special", height = 6, width = 6)
plot(x, y)dev.off()
@

\simplefig{\Sexpr{fig.name}}{Plot of the data.}

\clearpage

\section{Now to fit a linear regression}

Can print the summary regression output from R:

<<regression, echo=FALSE>>=
fit = lm(y~x)

print(summary(fit))
@ 

Can produce a simple table of output in Table \ref{tab:fit}, and the regression fit is shown in Figure \ref{fig:regfit}.

<<fit.table, results=tex, echo=FALSE>>=
print(xtable(fit, caption="Linear regression fit.", label=paste("tab:fit")))
@ 
\clearpage

<<echo=FALSE, results=hide>>=
fig.name = "regfit"
postscript(paste(fig.name, ".eps", sep=""), horizontal=FALSE, paper="special", height = 6, width = 6)
plot(x, y)
abline(fit, col="red")
dev.off()
@

\simplefig{\Sexpr{fig.name}}{Plot of the data with the fitted regression.}

<<save, echo=FALSE>>=
save.image(file=paste("sweaveExample.RData", sep=""))
@ 

\end{document}

% To stop before the end, need (uncommented):
% \end{document}
% <<>>=
% stop()
% @ 

-->


<!--
Maybe useful options, adapted from gfsynopsis:

```{r setup, echo=FALSE, cache=FALSE, message=FALSE, results='hide', warning=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  comment = "#>",
  fig.path = "knitr-figs/",
  cache.path = if (knitr:::is_latex_output()) "knitr-cache-tex/" else "knitr-cache-docx/",
  fig.asp = 0.618,
  fig.width = 9,
  out.width = "6in",
  echo = FALSE,
  autodep = TRUE,
  cache = TRUE,
  cache.comments = FALSE,
  dev = if (knitr:::is_latex_output()) "png" else "png",
  dpi = 200,
  fig.align = "center",
  fig.pos = "htb"
)
```

-->
