---
output:
  bookdown::pdf_book:
    toc: no
fontsize: 12pt
bibliography: references.bib
csl: ./tr-style/csas.csl
link-citations: true
header-includes:
  \usepackage{./tr-style/TechReport}
urlcolor: navyblue
---

<!-- To build from command line: rmarkdown::render("Proceedings.Rmd")  -->

<!-- File path to resources (e.g., style file, logos) -->
<!-- https://github.com/grinnellm/TechnicalReport -->
\newcommand{\locRes}{./tr-style}
<!-- We will eventually include this style file in csasdown -->

<!-- Title, year, report number -->
\newcommand{\trTitle}{Proceedings of the Technical Expertise in Stock Assessment
 (TESA) national workshop on `Tools for transparent, traceable, and transferable
 assessments', 27--30 November 2018 in Nanaimo, British Columbia}
\newcommand{\trYear}{YYYY}
\newcommand{\trReportNum}{NNNN}

<!-- Wrangle author names -->
```{r authors, warning=FALSE, message=FALSE, echo=FALSE}
# Require packages
require( tidyverse )

# Paste strings nicely
PasteNicely <- function( x, intChars=", ", nChar="and " ) {
  # Get the length of the vector
  n <- length( x )
  # If there are more than two 
  if( n > 2 ) {
    # Make a print-friendly vector
    x[n] <- paste( nChar, x[n], sep="" )
    # Get print friendly values
    res <- paste( x, collapse=intChars )
  } else {  # End if more than two, otherwise
    # Add a space
    nCharSp <- paste( " ", nChar, sep="" )
    # Get print friendly values
    res <- paste( x, collapse=nCharSp )
  }  # End if not more than two
  # Return the results
  return( res )
}  # End PasteNicely function

# Author names (use '~' between multi-part last names with spaces: de~la~Mare)
Authors <- c( "Andrew M. Edwards$^1$",
  "Daniel E. Duplisea$^2$",
  "Matthew H. Grinnell$^1$",
  "Sean C. Anderson$^1$",
  "Chris J. Grandin$^1$",
  "Daniel Ricard$^3$",
  "Elise A. Keppel$^1$",
  "Erika D. Anderson$^1$",
  "Krista D. Baker$^4$",
  "Hugues P. Beno\\^it$^2$",
  "Jaclyn S. Cleary$^1$",
  "Brendan M. Connors$^5$",
  "Mathieu Desgagn\\'es$^2$",
  "Philina A. English$^1$",
  "David J. Fishman$^3$",
  "Cameron Freshwater$^1$",
  "Kevin J. Hedges$^6$",
  "Carrie A. Holt$^1$",
  "Kendra R. Holt$^5$",
  "A.~Rob Kronlund$^7$",
  "Ann Mariscak$^1$",
  "Shannon G. Obradovich$^1$",
  "Bruce A. Patten$^1$",
  "Bob Rogers$^4$",
  "Chris N. Rooper$^1$",
  "Mark R. Simpson$^4$",
  "Tobie J. Surette$^3$",
  "Ross F. Tallman$^6$",
  "Laura J. Wheeland$^4$",
  "Catarina Wor$^1$", 
  "Xinhua Zhu$^6$" )

# Strip math stuff from author names
AuthorsNoMath <- gsub( pattern="\\$.*\\$", replacement="", x=Authors )

# Function to convert "First M. Last"" to "Last, F.M." for citations
Convert2Cite <- function( names ) {
  # Get last names, and make a list
  fam <- sub( pattern=".* ", replacement="", x=names ) %>%
    as.list( )
  # Pattern to search for initials
  regex <- '(?<=^|\\s)[[:alpha:]]' 
  # Get initials, drop the last one (family name), and collapse
  inits <- regmatches( x=names, 
    m=gregexpr(pattern=regex, text=names, perl=TRUE) ) %>%
    lapply( FUN=function(x) head(x, -1) ) %>%
    lapply( FUN=function(x) paste(x, collapse=".") )
  # Error if these aren't the same length
  if( length(fam) != length(inits) )
    stop( "Different length for family names and initials" )
  # Combine last name and initials, and add a trailing dot
  res <- fam %>%
    paste( inits, sep=", ") %>%
    paste( ".", sep="" )
  # Return the results
  return( res )
}  # End Convert2Cite function

# Get names for citaion
AuthorsBack <- Convert2Cite( names=AuthorsNoMath )
```

<!-- Authors -->
\newcommand{\trAuths}{`r PasteNicely(Authors)`}
\newcommand{\trAuthsNoMath}{`r PasteNicely(AuthorsNoMath)`}
\newcommand{\trAuthsBack}{`r PasteNicely(AuthorsBack)`}

<!-- Address -->
\newcommand{\trAddy}{
Pacific Biological Station\\
Fisheries and Oceans Canada\\
3190 Hammond Bay Road\\
Nanaimo, British Columbia\\
V9T 6N7}

<!-- Affiliations -->
\newcommand{\trAffil}{
$^1$Pacific Biological Station, Fisheries and Oceans Canada, 3190~Hammond Bay
Road, Nanaimo, British Columbia, V9T 6N7.\\
$^2$Maurice Lamontagne Institute, Fisheries and Oceans Canada, 850~route~de~la mer, Mont-Joli, Quebec, G5H 3Z4.\\
$^3$Gulf Fisheries Centre, Fisheries and Oceans Canada, 343~Universit\'e Avenue,
Moncton, New~Brunswick, E1C 9B6.\\
$^4$Northwest Atlantic Fisheries Centre, Fisheries and Oceans Canada, 80~East White Hills, St.~John's, Newfoundland and Labrador, A1C 5X1.\\
$^5$Institute of Ocean Sciences, Fisheries and Oceans Canada, P.O.~Box~6000,
9860~West Saanich Road, Sidney, British Columbia, V8L 4B2.\\
$^6$Freshwater Institute, Fisheries and Oceans Canada, 501~University Crescent, Winnipeg, Manitoba, R3T 2N6.\\
$^7$Centennial Towers, Fisheries and Oceans Canada, 200~Kent Street, 9th~floor, Ottawa, Ontario, K1A 0E6.
}

<!-- Abstract -->
\newcommand{\trAbstract}{
A four-day workshop was held in Nanaimo, British Colubmia, from 27--30
November 2018. The aim was to foster a
common understanding of modern computational methods and tools among stock
assessment scientists in Fisheries and
Oceans Canada (DFO). These tools enable efficient sharing of code and
writing of complex stock assessment documents within an assessment team, and
easy sharing of methods with other scientists.
This should lead to more
transparent, traceable, and transferable (TTT) assessments in DFO.

\emph{Transparent} means a clear and open way to show data, code, and
results, such that others should be able to reproduce the assessment.
\emph{Traceable} means that there is a clear link from database queries and code
to final results (numbers, tables, and
graphs in an assessment document).
\emph{Transferable} means that it should be feasible for another person to 
reproduce an assessment and build upon it with a minimal
learning curve. A fourth T could be
\emph{Translatable} in the sense that with two official languages, it is
important to ensure consistent translations
between official languages. 

Software demonstrations were given of Git, GitHub, R Markdown, knitr, LaTeX, 
and creation of R packages. For example, the csasdown R package was introduced 
to show how properly formatted documents produced for Canadian Science Advisory 
Secretariat (CSAS) processes can be built and elegantly updated with new assessment 
model results.

Presentations were given on
open data standards, on CSAS formatting and accessibility constraints, and on
GitLab (a Git service available to Government of Canada employees). Anticipated
changes to the Fisheries Act in 2019, particularly in relation to the need for
limit reference points, were discussed with respect to how TTT tools could
support the operationalisation of providing science advice in DFO.
Participants formed several breakout groups to practice using these tools,
creating, for example, an automated report from a multispecies survey, and an
R package to facilitate fast, cheap, and efficient translation of figures appearing in 
CSAS documents. This proceedings document was written collectively during the 
workshop using the TTT tools as a testament to the efficiency of this way of 
collaborative working.
}

<!-- Resume (i.e., French abstract) -->
\newcommand{\trResume}{
Un groupe de travail de 4 jours a eu lieu \`{a} Nanaimo, Colombie-Britanique, 
du 27 au 30 novembre 2018. L'objectif \'{e}tait de favoriser une compr\'{e}hension 
commune des outils et m\'{e}thodes modernes parmi les scientifiques en 
\'{e}valuation des stocks de P\^{e}ches et Oc\'{e}ans Canada (MPO). Ces outils 
permettent un \'{e}change efficace de code informatique et l'\'{e}criture de 
documents d'\'{e}valuations complexes \`{a} l'int\'{e}rieur d'une \'{e}quipe 
d'\'{e}valuation, et le partage facile de m\'{e}thodes avec d'autres scientifiques. 
Ceci devrait mener \`{a} des \'{e}valuations plus transparentes, tra\c{c}ables et 
transf\'{e}rables (TTT) au MPO.

\emph{Transparent}: Il existe un moyen clair et ouvert d'afficher des
donn\'{e}es, du code, et des r\'{e}sultats, et d'autres utilisateurs devraient
pouvoir reproduire l'\'{e}valuation; \emph{tra\c{c}able}: On devrait pouvoir
relier les r\'{e}sultats aux composantes de l'\'{e}valuation; et,
\emph{transf\'{e}rable}: Il devrait \^{e}tre possible \`{a} une autre personne
de se charger de l'\'{e}valuation et de l'innover avec une courbe
d'apprentissage minimale.  Un quatri\`{e}me T pourrait \^{e}tre
\emph{Traduisible} puisque avec deux langues officielles il est important de
s'assurer que les documents suivent un standard qui permet des traductions
consistentes entre les langues officielles.  

Des exemples de logiciels ont \'{e}t\'{e} pr\'{e}sent\'{e}s pour Git, GitHub, 
R Markdown, knitr, LaTeX et la cr\'{e}ation de composantes du logiciel R (R packages). 
Par exemple, le package csasdown a \'{e}t\'{e} pr\'{e}sent\'{e} pour montrer comment 
des documents correctement format\'{e}s produits durant les processus scientifiques du 
Secr\'{e}tariat Canadien de Consultation Scientifique (SCCS) peuvent \^{e}tre 
cr\'{e}\'{e}s et \'{e}l\'{e}gamment mis \`{a} jour avec de nouveaus r\'{e}sultats de 
mod\`{e}les d'\'{e}valuation. 

Des pr\'{e}sentations sur les standards de donn\'{e}es ouvertes, sur les contraintes 
de mise en page et d'accessibilit\'{e} du SCCS, et sur GitLab (un service Git 
accessible aux employ\'{e}(e)s du gouvernement du Canada) ont aussi eu lieu. 
Les changements anticip\'{e}s \`{a} la loi sur les p\^{e}ches en 2019, 
particuli\`{e}rement en ce qui \`{a} trait au besoin de 
points de r\'{e}f\'{e}rence, ont \'{e}t\'{e} discut\'{e}s par rapport au r\^{o}le
de support que pourrait jouer les outils TTT dans l'op\'{e}rationnalisation de
ces changements l\'{e}gislatifs pour fournir des avis scientifiques au MPO.  
Les participants ont form\'{e} plusieurs sous-groupes afin de pratiquer 
l'utilisation de ces outils, cr\'{e}ant, par exemple, un rapport automatis\'{e} 
d'un relev\'{e} multi-esp\`{e}ce, et un package R facilitant des traductions rapides, 
abordables et efficaces des figures apparaissant dans les documents SCCS. Le 
pr\'{e}sent rapport a \'{e}t\'{e} \'{e}crit collectivement durant le groupe de
travail en utilisant les outils TTT, un t\'{e}moignage de l'efficacit\'{e} de cette
mani\`{e}re de travailler collaborativement.
}

<!-- Make the first few pages -->
\frontmatter

<!-- Basic set up -->
```{r echo=FALSE, warning=FALSE, message=FALSE}
library(dplyr)
library(readr)
# https://github.com/haozhu233/kableExtra/issues/274
# avoid xcolor clash:
options(kableExtra.latex.load_packages = FALSE)
```

<!-- Introduction -->
```{r child='1_Introduction.Rmd'}
```

<!-- Day 1 -->
```{r child='2_Day1.Rmd'}
```

<!-- Day 2 -->
```{r child='3_Day2.Rmd'}
```

<!-- Day 3 -->
```{r child='4_Day3.Rmd'}
```

<!-- Day 4 -->
```{r child='5_Day4.Rmd'}
```

<!-- Conclusions -->
```{r child='6_Conclusions.Rmd'}
```

# REFERENCES {-}
<!--This manually sets the header for this unnumbered chapter.-->
\markboth{References}{References}

\noindent
\vspace{-2em}
\setlength{\parindent}{-0.2in}
\setlength{\leftskip}{0.2in}
\setlength{\parskip}{8pt}
