---
output:
  bookdown::pdf_book:
    toc: no
fontsize: 12pt
bibliography: references.bib
csl: ./tr-style/csas.csl
link-citations: true
header-includes:
  \usepackage{./tr-style/TechReport}
---

<!-- File path to resources (e.g., style file, logos) -->
<!-- https://github.com/grinnellm/TechnicalReport -->
\newcommand{\locRes}{./tr-style}

<!-- Title, year, report number -->
\newcommand{\trTitle}{Proceedings of the {TESA} workshop on tools for transparent, traceable, and transferable assessments}
\newcommand{\trYear}{YYYY}
\newcommand{\trReportNum}{NNNN}

<!-- Authors -->
\newcommand{\trAuthsLong}{Andrew Edwards, Daniel Duplisea}
\newcommand{\trAuthsBack}{Edwards, A, and Duplisea, D.}

<!-- Address -->
\newcommand{\trAddy}{Fisheries and Oceans Canada\\Science Branch, Pacific Region\\Pacific Biological Station\\3190 Hammond Bay Road\\Nanaimo, BC \enskip V9T 6N7}

<!-- Abstract -->
\newcommand{\trAbstract}{
A four day workshop was held in Nanaimo 27-30 Nov 2018 to foster a common understanding of modern methods and tools in DFO that enables an exchange of knowledge, data and methods for stock assessment which should lead to transparent, traceable, and transferable (TTT) assessments in DFO.
\emph{Transparent}: There is a clear and open way to show data, code and results and others should be able to duplicate the assessment;
\emph{Traceable}: One should be able to link results to components; and
\emph{Transferable}: It should be feasible for another person to pick up the assessment and build on it with a minimal learning curve.
A fourth T could be \emph{Translatable} in the sense that with two official languages, it is important to ensure proper document standards to enable consistent translations between official languages.
Software demonstrations were given of Git, Github, RMarkdown, knitr and LaTeX, and group work was conducted around the use of these tools.
For example csasdown styles were introduced to show how document produced for science processes through the Canadian Secretariat for Science Advice (\href{http://www.dfo-mpo.gc.ca/csas-sccs/index-eng.htm}{CSAS}) could be produced and updated using assessment model runs.
Presentations were given on open data standards, on CSAS formatting and accessibility constraints and on GitLab (a Git service available to Government of Canada employees).
Anticipated changes to the Fisheries Act in 2019, particularly in relation to the need for limit reference points, were discussed in relation to how TTT tools could support the operationalisation of these legislative changes in the DFO science advice.
The present report was written collectively during the workshop using the TTT tools as a testament to the efficacy of this way to work.
}

<!-- Resume (i.e., French abstract) -->
\newcommand{\trResume}{
Un groupe de travail de 4 jours a eu lieu \`{a} Nanaimo du 27 au 30 novembre 2018 afin de favoriser une compr\'{e}hension commune des outils et m\'{e}thodes modernes qui permettent un \'{e}change de connaissance, de donn\'{e}es et de m\'{e}thodes pour l'\'{e}valuation des stocks et qui conduira vers des {e}valuations transparentes, tra\c{c}ables et transf\'{e}rables (TTT) au MPO.
\emph{Transparent}: Il existe un moyen clair et ouvert d'afficher des donn\'{e}es, du code et des r\'{e}sultats, et d'autres utilisateurs devraient pouvoir reproduire l'\'{e}valuation;
\emph{tra\c{c}able}: On devrait pouvoir relier les r\'{e}sultats aux composantes de l'\'{e}valuation; et, 
\emph{transf\'{e}rable}: Il devrait \^{e}tre possible \`{a} une autre personne de se charger de l'\'{e}valuation et de l'innover avec une courbe d'apprentissage minimale.
Un quatri\`{e}me T pourrait \^{e}tre \emph{Traduisible} puisque avec deux langues officielles il est important de s'assurer que les documents suivent un standard qui permet des traductions consistentes entre les langues officielles.
Des exemples de logiciels ont \'{e}t\'{e} pr\'{e}sent\'{e}s pour Git, Github, RMarkdown, knitr et LaTeX, et le travail de groupe s'est concentr\'{e} sur l'utilisation de ces outils.
Par exemple, les styles csasdown ont \'{e}t\'{e} pr\'{e}sent\'{e}s pour montrer comment les documents produits durant les processus scientifiques du Secr\'{e}tariat Canadien de Consultation Scientifique (\href{http://www.dfo-mpo.gc.ca/csas-sccs/index-eng.htm}{SCCS}) pourraient \^{e}tre cr\'{e}\'{e}s et r\'{e}dig\'{e}s \`{a} l'aide des passes de mod\`{e}les d'\'{e}valuation.
Des pr\'{e}sentations sur les standards de donn\'{e}es ouvertes, sur les contraintes de mise en page et d'accessibilit\'{e} du SCCS et sur GitLab (un service Git accessible aux employ\'{e}(e)s du gouvernement du Canada) ont aussi eu lieu.
Les changements anticip\'{e}s de la loi sur les p\^{e}ches en 2019, particuli\`{e}rement en ce qui \`{a} trait au besoin de points de r\'{e}f\'{e}rence, a \'{e}t\'{e} discut\'{e} par rapport au r\^{o}le de support que pourrait jouer les outils TTT dans l'op\'{e}rationnalisation de ces changements l\'{e}gislatifs dans les avis scientifiques du MPO.
Le pr\'{e}sent rapport a \'{e}t\'{e} \'{e}crit collectivement durant le groupe de travail en utilisant les outils TTT, un testament de l'efficacit\'{e} de cette mani\`{e}re de travailler.
}
<!-- Make the first few pages -->
\frontmatter

<!-- Basic set up -->
```{r echo=FALSE, warning=FALSE, message=FALSE}
# Require packages
library( tidyverse )
library( knitr )
library( kableExtra )
library( bookdown )
library( bindrcpp )
```

<!-- Introduction -->
```{r child='1_Introduction.Rmd'}
```

<!-- Day 1 -->
```{r child='2_Day1.Rmd'}
```

<!-- Day 2 -->
```{r child='3_Day2.Rmd'}
```

<!-- Day 3 -->
```{r child='4_Day3.Rmd'}
```

<!-- Day 4 -->
```{r child='5_Day4.Rmd'}
```

<!-- Conclusions -->
```{r child='6_Conclusions.Rmd'}
```

# REFERENCES {-}
<!--This manually sets the header for this unnumbered chapter.-->
\markboth{References}{References}

\noindent
\vspace{-2em}
\setlength{\parindent}{-0.2in}
\setlength{\leftskip}{0.2in}
\setlength{\parskip}{8pt}

