---
output:
  bookdown::pdf_book:
    toc: no
fontsize: 12pt
header-includes:
  \usepackage{./tr-style/TechReport}
---

<!-- File path to resources (e.g., style file, logos) -->
<!-- https://github.com/grinnellm/TechnicalReport -->
\newcommand{\locRes}{./tr-style}

<!-- Title, year, report number -->
\newcommand{\trTitle}{Proceedings of the {TESA} workshop on tools for transparent, traceable, and transferable assessments}
\newcommand{\trYear}{YYYY}
\newcommand{\trReportNum}{NNNN}

<!-- Authors -->
\newcommand{\trAuthsLong}{Andrew Edwards, Daniel Duplisea}
\newcommand{\trAuthsBack}{Edwards, A, and Duplisea, D.}

<!-- Address -->
\newcommand{\trAddy}{Fisheries and Oceans Canada\\Science Branch, Pacific Region\\Pacific Biological Station\\3190 Hammond Bay Road\\Nanaimo, BC \enskip V9T 6N7}

<!-- Abstract -->
\newcommand{\trAbstract}{
\trTitle, 27 to 30 {November} 2018 in Nanaimo, BC.}

<!-- Resume (i.e., French abstract) -->
\newcommand{\trResume}{
Et en fran\c{c}ais...}

<!-- Make the first few pages -->
\frontmatter

<!-- Basic set up -->
```{r echo=FALSE, warning=FALSE, message=FALSE}
# Require packages
library( tidyverse )
library( knitr )
library( kableExtra )
library( bookdown )
library( bindrcpp )
```

<!-- Introduction -->
```{r child='1_Introduction.Rmd'}
```

<!-- Day 1 -->
```{r child='2_Day1.Rmd'}
```

<!-- Day 2 -->
```{r child='3_Day2.Rmd'}
```

<!-- Day 3 -->
```{r child='4_Day3.Rmd'}
```

<!-- Day 4 -->
```{r child='5_Day4.Rmd'}
```

<!-- Conclusions -->
```{r child='6_Conclusions.Rmd'}
```
